Unsupervised Detection and Tracking of Arbitrary Objects with Dependent Dirichlet Process Mixtures

### 2012-03-15 ltx/paper_uai.tex
newest version. main difference: removal of sensitivity analysis figures, lots of edits

\documentclass[twocolumn, final]{svjour3}
\usepackage[square,numbers]{natbib}
\usepackage{amsmath, epsfig}
\usepackage{amsfonts}
\usepackage{graphicx}
\usepackage{amsfonts}
\usepackage{algorithm}
\usepackage{algorithmic}
\usepackage{easybmat}
\usepackage{footmisc}
\usepackage[usenames,dvipsnames]{color}
\usepackage{subfig}
\renewcommand\algorithmiccomment[1]{// \textit{#1}}
\newcommand{\ignore}[1]{}
\newcommand{\comment}[1]{}
\newcommand{\frank}[1]{\textcolor{red}{\textsf{\emph{\textbf{\textcolor{blue}{#1}}}}}}
\newcommand{\willie}[1]{\textcolor{green}{\textsf{\emph{\textbf{\textcolor{green}{#1}}}}}}
\DeclareMathOperator*{\argmax}{arg\,max}

@@

\title{Unsupervised Detection and Tracking of Arbitrary Objects with Dependent Dirichlet Process Mixtures}
\titlerunning{Unsupervised Detection and Tracking of Arbitrary Objects with Dependent Dirichlet Process Mixtures}
\author{Willie Neiswanger$^{*}$ and Frank Wood$^{\dagger}$}
\authorrunning{Willie Neiswanger and Frank Wood}
\institute{ $^{*}$Columbia University, Department of Applied Math and Applied Physics. Tel.: 503-464-6152. \email{wdn2101@columbia.edu} \and $^{\dagger}$Columbia University, Department of Statistics. Tel.: 212-851-2150. \email{fwood@stat.columbia.edu}}
\date{}  % add submit date when submitted
\maketitle

@@

We desire a data extraction procedure that yields observations of the form
\begin{equation}
\centering
\bold{x} = ( \bold{x}^{s}, \bold{x}^{c}, t ) = ( x^{s_{1}}, x^{s_{2}}, x^{c_{1}}, \ldots, x^{c_{V}}, t )
\end{equation}
where each $\bold{x}$ corresponds to a point within an image region where an object (or foreground element)  is believed to exist, $\bold{x}^{s} \in \mathbb{R}^{2}$ denotes the spatial location of this point, $\bold{x}^{c} \in S_{1} \times \ldots \times S_{V}$ denotes some collection of local image characteristics in the vicinity of this point, and $t \in \{1, \ldots, T \}$ denotes the time index.

@@

In \cite{ellis_2010}, performance metrics (including the SFDA and ATA) were computed for a number of studies that carried out object detection and tracking for the PETS20-\\09/2010 dataset. As this dataset consists solely of humans, all ten of the algorithms presented for comparison were developed for the specific purpose of people tracking (i.e. not for general detection and tracking of arbitrary objects). In consequence, many of these studies use externally developed (and trained) state-of-the-art human detectors, exploit the orientation of the humans in this specific dataset, or apply motion models based on assumptions about human motion. We compare SFDA and ATA results of our strategy with these methods to show that our arbitrary object framework can yield comparable results even when compared with object-specific trackers. Table~\ref{benchmark_results_table} shows performance metric results for comparison (data published with permission from the authors of \cite{ellis_2010}).

>>>>

% \documentclass[twocolumn, final]{svjour3}
\documentclass{article}
\usepackage{proceed}
\usepackage[square,numbers]{natbib}
\usepackage{amsmath, epsfig}
\usepackage{amsfonts}
\usepackage{graphicx}
\usepackage{amsfonts}
\usepackage{algorithm}
\usepackage{algorithmic}
\usepackage{easybmat}
\usepackage{footmisc}
\usepackage[usenames,dvipsnames]{color}
\usepackage{subfig}
\renewcommand\algorithmiccomment[1]{// \textit{#1}}
\newcommand{\ignore}[1]{}
\newcommand{\comment}[1]{}
\newcommand{\frank}[1]{\textcolor{red}{\textsf{\emph{\textbf{\textcolor{blue}{#1}}}}}}
\newcommand{\willie}[1]{\textcolor{green}{\textsf{\emph{\textbf{\textcolor{green}{#1}}}}}}
\DeclareMathOperator*{\argmax}{arg\,max}

@@

\title{Unsupervised Detection and Tracking of Arbitrary Objects with Dependent Dirichlet Process Mixtures}
% \titlerunning{Unsupervised Detection and Tracking of Arbitrary Objects with Dependent Dirichlet Process Mixtures}
\author{Willie Neiswanger$^{*}$ and Frank Wood$^{\dagger}$}
% \authorrunning{Willie Neiswanger and Frank Wood}
% \institute{ $^{*}$Columbia University, Department of Applied Math and Applied Physics. Tel.: 503-464-6152. \email{wdn2101@columbia.edu} \and $^{\dagger}$Columbia University, Department of Statistics. Tel.: 212-851-2150. \email{fwood@stat.columbia.edu}}
% \date{}  % add submit date when submitted
\maketitle

@@

We desire a data extraction procedure that yields observations of the form
\begin{equation}
\centering
\bold{x} = ( \bold{x}^{s}, \bold{x}^{c}, t ) = ( x^{s_{1}}, x^{s_{2}}, x^{c_{1}}, \ldots, x^{c_{V}}, t )
\end{equation}
where each $\bold{x}$ corresponds to a point within an image region where an object (or foreground element)  is believed to exist, $\bold{x}^{s} \in \mathbb{R}^{2}$ denotes the spatial location of this point, $\bold{x}^{c} \in S_{1} \times \ldots \times S_{V}$ denotes some collection of local image features in the vicinity of this point, and $t \in \{1, \ldots, T \}$ denotes the time index.

@@

In \cite{ellis_2010}, performance metrics (including the SFDA and ATA) were computed for a number of studies that carried out object detection and tracking for the PETS20-\\09/2010 dataset. As this dataset consists solely of humans, all ten of the algorithms presented for comparison were developed for the specific purpose of people tracking (i.e. not for general detection and tracking of arbitrary objects). In consequence, many of these studies use externally developed (and trained) state-of-the-art human detectors, exploit the orientation of the humans in this specific dataset, or apply motion models based on assumptions about human motion. We compare SFDA and ATA results of our strategy with these methods to show that our arbitrary object framework can yield comparable results even when compared with object-specific trackers. Table~\ref{benchmark_results_table} shows performance metric results for comparison (data published with permission from the authors of \cite{ellis_2010}). Our method achieves the fourth best SFDA and third best ATA.

The algorithm in \cite{breitenstein2009markovian} is based around output from an externally made human detector; in \cite{yang2009probabilistic}, assumptions about the orientation and appearance of clothing on humans is used; and in
